### 2020-05-28 myThesis/thesis_LaTeX/main.tex
thesis re-organisation
biber now working
quote

\documentclass[
% The default document font size, options: 10pt, 11pt, 12pt
11pt, 
% Two side (alternating margins) for binding by default, uncomment to switch to one side
oneside,
% ngerman for German
english,
% Single line spacing, alternatives: singlespacing, onehalfspacing or doublespacing
onehalfspacing,
% Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%draft,
% If the document is nolistspacing, onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
onehalfspacing,
% Uncomment to add the list of figures/tables/etc to the table of contents
%liststotoc,
% Uncomment to add the main table of contents to the table of contents
%toctotoc,
% Uncomment to add space between paragraphs
parskip,
% Uncomment to not load the hyperref package
%nohyperref,
% Uncomment to get a line under the header
headsepline,
% Uncomment to place the chapter title next to the number on one line
chapterinoneline,
% Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
consistentlayout,
% The class file specifying the document structure
]{MastersDoctoralThesis}

@@

@@

@@

To my mother, Helena, who continues to learn, grow and develop and who has been a
source of encouragement and inspiration to me throughout my life, a very special
thank you for providing a ‘writing space’ and for nurturing me through the months of
writing. And also for the myriad of ways in which, throughout my life, you have
actively supported me in my determination to find and realise my potential, and to
make this contribution to our world.\\

To my mother-in-law, Maryam, known only briefly but loved and missed, who
represented to me ‘living proof’ of Black women’s ability to redefine and recreate our
lives despite, and maybe even because of, the tremendously constraining, oppressive
and repressive situations in which we often exist.\\

To my dear husband, Bala who remains willing to engage with the struggle, and
ensuing discomfort, of having a partner who refuses to accept the given role of the
"Black woman" and is actively engaged in redefining and redesigning that role. A
very special thank you for your practical and emotional support as I added the roles of
wife and then mother, to the competing demands of business, work, study and
personal development.\\

Thanks to dear Kamal and Azaria, for being so supportive - even when being ‘without
Mum’ was hard, and for your help with the bibliography and diagrams. This work is
for, and because of you and all the generations to come. It is dedicated to all our
journeys in learning to thrive.\\

It is also dedicated to Josephine - friend, ‘sister’, colleague, ‘co- traveller’ and
researcher - who knowingly and unknowingly- led me to an understanding of some of
the more subtle challenges to our ability to thrive. If our attempts to claim our right to
speak our truth, and to unravel and follow the threads through which our oppression is
maintained, and are instrumental in helping one other Black woman from ‘going over
the edge’ - in which sight we continuously live our lives - perhaps, it might be seen
that your invaluable contribution to the attainment of many of the insights gained was
worth it. It is also written in honour of all our my grandmothers, and their mothers,
and grandmothers, and to all our and mothers and grandmothers, who though not
marked by history struggled so heroically to resist the definitions attributed to them
by the dominant system and communicate messages of hope and expectation.
I am also very grateful to Maya Angelou, for the inspiration she has been to methrough her writings, poetry readings and as a living representation of a woman
thriving. Thanks to Mary Washington, Alice Walker, Jackie Kay, Buchi Emecheta,
Toni Cade, Lauretta Ngobo, bell hooks, and other Black women writers of the 1980’s,
who in telling stories for and about us validated me and my experiences in ways I
cannot begin to explain here.\\

Loving thanks to my friends / learning partners, Agnes, Susan, Ulana and Namonya,
who played such important roles along the journey, as we mutually engaged in
making sense of the various challenges we faced and in providing encouragement to
each other at those times when it seemed impossible to continue. I offer my gratitude
and appreciation to my supervisors, Judi Marshall and Peter Reason, for the deft ways
in which you lovingly challenged and supported me through out the whole of this
work - knowing when to push and when to let up. I offer special thanks to those who
supported me in the mechanics of producing this thesis. Rosemary, for reading and rereading drafts; Rajwant for editing and proofing; Susan for help with typing and for
helping me get ‘unstuck’ with this thesis on many occasions; and Peter and Trevor for
‘rescuing’ me at those times when I was almost defeated by the technology. Most of
all thanks to God the Divine who continues to make the impossible possible.

@@

>>>>

\documentclass[
% The default document font size, options: 10pt, 11pt, 12pt
11pt, 
% Two side (alternating margins) for binding by default, uncomment to switch to one side
oneside,
% ngerman for German
english,
% Single line spacing, alternatives: singlespacing, onehalfspacing or doublespacing
onehalfspacing,
% Uncomment to enable draft mode (no pictures, no links, overfull hboxes indicated)
%draft,
% If the document is nolistspacing, onehalfspacing or doublespacing, uncomment this to set spacing in lists to single
onehalfspacing,
% Uncomment to add the list of figures/tables/etc to the table of contents
%liststotoc,
% Uncomment to add the main table of contents to the table of contents
%toctotoc,
% Uncomment to add space between paragraphs
parskip,
% Uncomment to not load the hyperref package
%nohyperref,
% Uncomment to get a line under the header
headsepline,
% Uncomment to place the chapter title next to the number on one line
%chapterinoneline,
% Uncomment to change the layout of the declaration, abstract and acknowledgements pages to match the default layout
%consistentlayout,
% The class file specifying the document structure
]{MastersDoctoralThesis}

@@

% stop all hyphenation
%\raggedright
\sloppy
\usepackage[none]{hyphenat}

@@

%----------------------------------------------------------------------------------------
%	QUOTATION PAGE
%----------------------------------------------------------------------------------------

\vspace*{0.2\textheight}

\begin{center}
\includegraphics[width=0.60\textwidth]{./Figures/quote.png}

\noindent\enquote{\itshape No great discovery was ever made without a bold guess.}\bigbreak
\end{center}

\begin{flushright}
\textbf{Newton, Sir Isaac} \linebreak
In W.I.B. Beveridge \linebreak
\emph{The Art of Scientific Investigation} \linebreak
Scientist (p. 145)
\end{flushright}

@@

% To my mother, Helena, who continues to learn, grow and develop and who has been a source of encouragement and inspiration to me throughout my life, a very special thank you for providing a ‘writing space’ and for nurturing me through the months of writing. And also for the myriad of ways in which, throughout my life, you have actively supported me in my determination to find and realise my potential, and to make this contribution to our world.\\

% To my mother-in-law, Maryam, known only briefly but loved and missed, who represented to me ‘living proof’ of Black women’s ability to redefine and recreate our lives despite, and maybe even because of, the tremendously constraining, oppressive and repressive situations in which we often exist.\\

% To my dear husband, Bala who remains willing to engage with the struggle, and ensuing discomfort, of having a partner who refuses to accept the given role of the "Black woman" and is actively engaged in redefining and redesigning that role. A very special thank you for your practical and emotional support as I added the roles of wife and then mother, to the competing demands of business, work, study and personal development.\\

% Thanks to dear Kamal and Azaria, for being so supportive - even when being ‘without Mum’ was hard, and for your help with the bibliography and diagrams. This work is for, and because of you and all the generations to come. It is dedicated to all our journeys in learning to thrive.\\

% It is also dedicated to Josephine - friend, ‘sister’, colleague, ‘co- traveller’ and researcher - who knowingly and unknowingly- led me to an understanding of some of the more subtle challenges to our ability to thrive. If our attempts to claim our right to speak our truth, and to unravel and follow the threads through which our oppression is maintained, and are instrumental in helping one other Black woman from ‘going over the edge’ - in which sight we continuously live our lives - perhaps, it might be seen that your invaluable contribution to the attainment of many of the insights gained was worth it. It is also written in honour of all our my grandmothers, and their mothers, and grandmothers, and to all our and mothers and grandmothers, who though not marked by history struggled so heroically to resist the definitions attributed to them by the dominant system and communicate messages of hope and expectation. I am also very grateful to Maya Angelou, for the inspiration she has been to methrough her writings, poetry readings and as a living representation of a woman thriving. Thanks to Mary Washington, Alice Walker, Jackie Kay, Buchi Emecheta, Toni Cade, Lauretta Ngobo, bell hooks, and other Black women writers of the 1980’s, who in telling stories for and about us validated me and my experiences in ways I cannot begin to explain here.\\

% Loving thanks to my friends and learning partners, Agnes, Susan, Ulana and Namonya, who played such important roles along the journey, as we mutually engaged in making sense of the various challenges we faced and in providing encouragement to each other at those times when it seemed impossible to continue.

I offer my gratitude and appreciation to my supervisors, \supname and \cosupname, for the deft ways in which you lovingly challenged and supported me through out the whole of this work - knowing when to push and when to let up. I offer special thanks to those who supported me in the mechanics of producing this thesis. \supname, for reading and rereading drafts, editing and proofing, typing and helping me get ‘unstuck’ with this thesis on many occasions. And Braulio and Arnoldo for ‘rescuing’ me at those times when I was almost defeated by the laboratory equipment.

@@

%% https://www.overleaf.com/learn/latex/bibtex_bibliography_styles
%% abbrv, acm, alpha, apalike, ieeetr, plain, siam, unsrt
%\bibliographystyle{plain}
%\renewcommand\bibname{References}
%\bibliography{mainBiblio}
